Verifying Demonstrations

### 2018-05-31 paper/conclusions.tex
removed redundancies in discussion, made subsections, changed title, added conclusion

Finally, most of the current methods are estimates, with quite some error 
margins. While \PRIVO is an actual count and not an estimate, its
accuracy for the total number of participants hinges on the
participants having the necessary equipment (a smartphone or similar
device), some sort of trustworthy credential, and the willingness to
run the protocol. Owing to the network effect, until used by most participants, \PRIVO would result in a
considerable undercount. However, it presents a first
step toward accurate verifiable yet privacy-preserving crowd counting
by showing how it can be done in theory at least and in practice once
some assumptions become more realistic.

>>>>

Finally, most of the current methods are estimates, with quite some
error margins. While \PRIVO is an actual count and not an estimate,
its accuracy for the total number of participants hinges on the
participants having the necessary equipment (a smartphone or similar
device), some sort of trustworthy credential, and the willingness to
run the protocol. Owing to the network effect, until used by most
participants, \PRIVO would result in a considerable
undercount. However, it presents a first step toward accurate
verifiable yet privacy-preserving crowd counting by showing how it can
be done in theory at least and in practice once some assumptions
concerning hardware and e-identities become more realistic. While the
the necessary technologies are not yet available in most authoritarian
regimes, some of them are in several democracies. We believe that it
is important to implement systems such as ours also there to support
the maintenance of democratic processes.
